---
title: "WHO Life Expectancy"
subtitle: "Project Proposal"
author: "Team name <br> Hannah, Joana and Max"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(janitor)
library(forcats)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
life_exp <- read_csv("Data/Life Expectancy Data.csv") %>%
  clean_names()

```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/park.jpg"
)
```

class: center, middle

# To investigate and compare species diversity in 56 different US national parks and investigating which factors might affect diversity.

.footnote[
Title Slide Image: KUONI 
]
---

class: inverse, center, middle

# Introduction

---

# The Data

- 'Life Expectancy (WHO)' available on Kaggle, collected from the World Health Organisation (WHO) and United Nations website

- One dataset "Life Expectancy Data.csv"

---
Data Glimpse
```{r echo=FALSE}
glimpse(life_exp)

```

---

class: inverse, center, middle

#Data Analysis Plan


---
#variables

The variables we are using are:

- Park name 

- Acres 

- Category 

- Order 

- Family 

- Common names 

- Occurrence 

- Abundance

---
#Investigation and Plot Ideas

- Investigate life expectancy vs development

- Look at how the life expectancy of a particular developed and developing country and see how it has changed over time

- Specific investigation into the effect of a high infant mortality on life expectancy

---
#Some Summary Statistics

Below is a table showing some summary statistics about the number of distinct species in the parks.

```{r echo = FALSE}



```

We can see there is quite a big variation in these, our question we are going to focus on is why?
---
#Initial visualisation

```{r echo = FALSE}

```



---

  