---
title: "Biodeversity in US National Parks"
subtitle: "Project Proposal"
author: "Team name <br> Hannah, Joana and Max"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(janitor)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
parks <- read_csv("Data/parks.csv") %>%
  clean_names()
species <- read_csv("Data/species.csv") %>%
  clean_names()

```

```{r include=FALSE}
style_xaringan(
  title_slide_background_image = "img/park.jpg"
)
```

class: center, middle

# To investigate and compare species diversity in 56 different US national parks and investigating which factors might affect diversity.

.footnote[
Title Slide Image: KUONI 
]
---

class: inverse, center, middle

# Introduction

---

# The Data

- 'Biodiversity in National Parks' available on Kaggle, collected from the US National Park Service database 

- Two data sets, parks.csv and species.csv that will need to be joined

---

# Data Glimpse - parks

```{r include=TRUE}
glimpse(parks)
```
---
#Data Glimpse - species
```{r include=TRUE}
glimpse(species)
```
---

class: inverse, center, middle

#Data Analysis Plan


---
#variables

The variables we are using are:

- Park name 

- Acres 

- Category 

- Order 

- Family 

- Common names 

- Occurrence 

- Abundance

---
#Plot Ideas

- Investigate how park area affects number of distinct species

- The effect of conservation on diversity

- Count of species abundance in a smaller selection of parks

---
#Some Summary Statistics

Below is a table showing some summary statistics about the number of distinct species in the parks.

```{r echo = FALSE}
species %>%
  filter(occurrence == "Present")%>%
  group_by(park_name)%>%
  summarise(n = n_distinct(species_id))%>%
  arrange(desc(n))%>%
  summarise(max = max(n), 
            min = min(n),
            mean = mean(n))


```

We can see there is quite a big variation in these, our question we are going to focus on is why?
---