---
title: "WHO Life Expectancy"
subtitle: "Project Proposal"
author: "Team name <br> Hannah, Joana and Max"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(janitor)
library(forcats)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
life_exp <- read_csv("Data/Life Expectancy Data.csv") %>%
  clean_names()

```

```{r include=FALSE}
style_xaringan(
)
```

class: center, middle

# To investigate and compare the life expectancy of countries of different social and economic status and investigate the main factors affecting life expectancy.

.footnote[
Title Slide Image: KUONI 
]
---

class: inverse, center, middle

# Introduction

---

# The Data

- 'Life Expectancy (WHO)' available on Kaggle, collected from the World Health Organisation (WHO) and United Nations website

- One dataset "Life Expectancy Data.csv"

---
Data Glimpse
```{r glimpse, echo=FALSE}
glimpse(life_exp)
```

---

class: inverse, center, middle

#Data Analysis Plan


---
#Variables

The variables we will mostly be using are:

- country
- year
- population
- life_expectancy
- status = Developed or Developing status
- schooling = Number of years of Schooling(years)
- income_composition_of_resources = Human Development Index (index ranging from 0 to 1)
- gdp = Gross Domestic Product per capita (in USD)
- adult_mortality = Adult Mortality Rates (probability of dying between 15 and 60 years per 1000 population)
- infant deaths = Number of Infant Deaths per 1000 population
- bmi = Average Body Mass Index of entire population
- total expendature = General government expenditure on health as a percentage of total government expenditure (%)
- alcohol = Alcohol, recorded per capita (15+) consumption (in litres of pure alcohol)

---
#Summary Statistics - Life expectancy in 2000 and 2015

Below is a table showing some summary statistics about the life expectancy of countries in the year 2000, by their development status

```{r summary stats 2000, echo = FALSE}
life_exp %>%
  filter(year == "2000")%>%
  group_by(status)%>%
  summarise(min = min(life_expectancy),
            max = max(life_expectancy),
            mean = mean(life_expectancy))


```

Below shows the same statistics but for 2015:
```{r summary stats 2015, echo = FALSE}
life_exp %>%
  filter(year == "2015")%>%
  group_by(status)%>%
  summarise(min = min(life_expectancy),
            max = max(life_expectancy),
            mean = mean(life_expectancy))
```
There is clearly a large difference in these values, our project will try to discover why.
---
#Discussion on Summary Statistics

There are some interesting features about the dataset that can be seen with these summary statistics.

- There exist developing countries with a higher life expectancy than some developed countries.

- Why is the range of the life expectancy in developing countries so much larger than that of developed?
---
#Investigation and Plot Ideas From These Initial Observations

- Look at how the life expectancy of a particular developed and developing country and see how they changed with time

- Specific investigation into the effect of a high infant mortality on life expectancy 

- Investigate why certain developing countries actually have a high life expectancy


---
#Afghanistan Life Expectancy 2000-2015
.pull-left[
- We can see from the visualisation on the previous slide that the life expectancy is increasing over time

- This is consistent with the summary statistics calculated earlier.
]
.pull-right[
```{r Afghanistan Graph, echo=FALSE, fig.width=4, warning=FALSE, out.width="100%"}
life_exp %>%
  filter(country == "Afghanistan")%>%
  ggplot(mapping = 
           aes(x = year, 
               y = life_expectancy))+
  geom_line()+
  labs(x = "Year",
       y = "Life Expectancy (years)")
```
]
---
#Distribution of Life Expectancy 2000
.pull-left[

- We can see that it is left skewed

- Developing countries seem to have a very wide range of life expectancies

- We can see that we have observations for many more developing countries than developed

- Clearly shows the large range of developing country life expectancy compared to the range for developed countries that we were introduced to with the summary statistics
]
.pull-right[
```{r echo=FALSE, fig.width=4, warning=FALSE, out.width="100%"}
life_exp %>%
  filter(year == 2000)%>%
  ggplot(mapping = 
           aes(x = life_expectancy))+
  geom_histogram(binwidth = 1, mapping = aes(fill = status))+
  labs(x = "Life Expectancy (years)",
       y = "Count",
       fill = "Status")
``` 
]
---
 